---
title: "OFC muscimol behavior (Figs 4, S4)"
author: "Matheus Macedo-Lima"
date: "2024-05-29"
output: html_document
---

# Load libraries and data
```{r echo=TRUE}
library(ggplot2)
library(dplyr)
library(tidyr)
# install.packages(c('remotes', 'TMB'))
# remotes::install_github("glmmTMB/glmmTMB/glmmTMB", build_vignettes=FALSE)
library(glmmTMB)
library(DHARMa)
library(car)
library(reshape2)
library(emmeans)
library(rcompanion)
# Create the notin operator
`%notin%` <- Negate(`%in%`)

# Some global plot parameters if modification is needed.
source('./r_theme.r', echo=F)
theme_set(theme_mml(base_size = 20))
LINE_THICKNESS = 1
ERRORBAR_THICKNESS = LINE_THICKNESS/2
INDIVIDUAL_DATAPOINT_LINE = LINE_THICKNESS/1.5
SMALL_PLOTS_LINE_THICKNESS = LINE_THICKNESS/3

cbPalette = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#d55e00")
treatment_colors = c('#0072B2', '#B9519E')

boxplot_whiskers <- function(x) {
  r <- quantile(x, probs = c(0.10, 0.25, 0.5, 0.75, 0.90))
  names(r) <- c("ymin", "lower", "middle", "upper", "ymax")
  r
}

response_bias = function(Hit, Miss, Reject, False_alarm) {
  hr = (Hit + 0.5) / (Hit + Miss + 1)
  far = (False_alarm+0.5)/(False_alarm+Reject+1)
  
  return( -0.5 * (qnorm(hr) + qnorm(far)) )
}


get_dprime = function(hr, far) {
  return( 
      qnorm(hr) - qnorm(far)
  )
}

boxplot_whiskers <- function(x) {
  r <- quantile(x, probs = c(0.10, 0.25, 0.5, 0.75, 0.90))
  names(r) <- c("ymin", "lower", "middle", "upper", "ymax")
  r
}

# Create the notin operator
`%notin%` <- Negate(`%in%`)

### Load previously saved dataframe
df = read.csv('./Data/Behavior_OFCmuscimol/Behavior_OFCmuscimol_df.csv')
df$Treatment = factor(df$Treatment, levels=c('Saline', 'Muscimol'))
```

# Fig 4C-H: OFC inactivation impairs AM detection behavior
## Fig 4C: d'
```{r echo=TRUE, fig.height=6, fig.width=3, warning=FALSE}
graph_data = df

y_axis = seq(-1, 3, 1)
p = ggplot(data=graph_data, aes(x=Treatment, y=D_prime, fill=Treatment, color=Treatment)) + 
  stat_summary(fun.data=boxplot_whiskers, geom="boxplot", na.rm = T, alpha=0.1, lwd=LINE_THICKNESS/6, fatten=1)+
  geom_line(aes(group = Subject, linetype=Hemisphere), color='black', alpha=0.1, size=LINE_THICKNESS/4) +
  ylab('d\'') +
  xlab('') +
  scale_fill_manual(name = "Treatment",
                   values = treatment_colors) +
  scale_color_manual(name = "Treatment",
                   values = treatment_colors) +
    
  scale_y_continuous(breaks=y_axis, expand=c(0, 0)) +
  coord_cartesian(ylim = c(min(y_axis), max(y_axis))) +
        
  annotate("text", x=1.5, y=2.8, label='Saline', color=treatment_colors[1], size=5, hjust=0) + 
  annotate("text", x=1.5, y=2.5, label='Muscimol', color=treatment_colors[2], size=5, hjust=0) + 
    
  theme(
    legend.position = 'none',
    axis.title.x=element_blank(),
    axis.line.x = element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p
```

### Stats
```{r echo=TRUE}
lme_data = graph_data
lme_bin <- glmmTMB(D_prime~Treatment + (1 | Subject) , data=lme_data, family=gaussian)
simulationOutput <- simulateResiduals(fittedModel = lme_bin, plot = T, re.form=NULL)  # pass
Anova(lme_bin)
```

## Fig 4D: Water consumption
```{r echo=TRUE, fig.height=6, fig.width=3, warning=FALSE}
graph_data = df

y_axis = seq(0, 1.2, 0.4)
p = ggplot(data=graph_data, aes(x=Treatment, y=WaterConsumed, fill=Treatment, color=Treatment)) + 
  stat_summary(fun.data=boxplot_whiskers, geom="boxplot", na.rm = T, alpha=0.1, lwd=LINE_THICKNESS/6, fatten=1)+
  geom_line(aes(group = Subject, linetype=Hemisphere), color='black', alpha=0.1, size=LINE_THICKNESS/4) +
  ylab('Water consumed (mL)') +
  xlab('') +
  scale_fill_manual(name = "Treatment",
                   values = treatment_colors) +
  scale_color_manual(name = "Treatment",
                   values = treatment_colors) +
    
  scale_y_continuous(breaks=y_axis, expand=c(0, 0)) +
  coord_cartesian(ylim = c(min(y_axis), max(y_axis))) +
      annotate("text", x=1.5, y=1.15, label='Saline', color=treatment_colors[1], size=5, hjust=0) + 
  annotate("text", x=1.5, y=1.11, label='Muscimol', color=treatment_colors[2], size=5, hjust=0) + 
    
  theme(
    legend.position = 'none',
    axis.title.x=element_blank(),
    axis.line.x = element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p
```

### Stats
```{r echo=TRUE}
lme_data = graph_data
lme_bin <- glmmTMB(WaterConsumed~Treatment + (1 | Subject) , data=lme_data, family=gaussian)
simulationOutput <- simulateResiduals(fittedModel = lme_bin, plot = T, re.form=NULL)  # pass
Anova(lme_bin)
```

## Fig 4E: Number of AM trials
```{r echo=TRUE, fig.height=6, fig.width=3, warning=FALSE}
graph_data = df

y_axis = seq(0, 60, 20)
p = ggplot(data=graph_data, aes(x=Treatment, y=N_Trials, fill=Treatment, color=Treatment)) + 
  stat_summary(fun.data=boxplot_whiskers, geom="boxplot", na.rm = T, alpha=0.1, lwd=LINE_THICKNESS/6, fatten=1)+
  geom_line(aes(group = Subject, linetype=Hemisphere), color='black', alpha=0.1, size=LINE_THICKNESS/4) +
  ylab('Num. AM trials') +
  xlab('') +
  scale_fill_manual(name = "Treatment",
                   values = treatment_colors) +
  scale_color_manual(name = "Treatment",
                   values = treatment_colors) +
    
  scale_y_continuous(breaks=y_axis, expand=c(0, 0)) +
  coord_cartesian(ylim = c(min(y_axis), max(y_axis))) +
    
  annotate("text", x=1.5, y=58, label='Saline', color=treatment_colors[1], size=5, hjust=0) + 
  annotate("text", x=1.5, y=55, label='Muscimol', color=treatment_colors[2], size=5, hjust=0) + 
    
  theme(
    legend.position = 'none',
    axis.title.x=element_blank(),
    axis.line.x = element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p
```

### Stats
```{r echo=TRUE}
lme_data = graph_data
lme_bin <- glmmTMB(N_Trials~Treatment + (1 | Subject) , data=lme_data, family=gaussian)
simulationOutput <- simulateResiduals(fittedModel = lme_bin, plot = T, re.form=NULL)  # pass
Anova(lme_bin)
```

## Fig 4F:AM trials per minute
```{r echo=TRUE, fig.height=6, fig.width=3, warning=FALSE}
graph_data = df

y_axis = seq(0, 10, 2)
p = ggplot(data=graph_data, aes(x=Treatment, y=Trial_rate_per_min, fill=Treatment, color=Treatment)) + 
  stat_summary(fun.data=boxplot_whiskers, geom="boxplot", na.rm = T, alpha=0.1, lwd=LINE_THICKNESS/6, fatten=1)+
  geom_line(aes(group = Subject, linetype=Hemisphere), color='black', alpha=0.1, size=LINE_THICKNESS/4) +
  ylab('AM trials / minute') +
  xlab('') +
  scale_fill_manual(name = "Treatment",
                   values = treatment_colors) +
  scale_color_manual(name = "Treatment",
                   values = treatment_colors) +
    
  scale_y_continuous(breaks=y_axis, expand=c(0, 0)) +
  coord_cartesian(ylim = c(min(y_axis), max(y_axis))) +
    
  annotate("text", x=1.5, y=9.8, label='Saline', color=treatment_colors[1], size=5, hjust=0) + 
  annotate("text", x=1.5, y=9.4, label='Muscimol', color=treatment_colors[2], size=5, hjust=0) + 
    
  theme(
    legend.position = 'none',
    axis.title.x=element_blank(),
    axis.line.x = element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p
```

### Stats
```{r echo=TRUE}
lme_data = graph_data
lme_bin <- glmmTMB(Trial_rate_per_min~Treatment + (1 | Subject) , data=lme_data, family=gaussian)
simulationOutput <- simulateResiduals(fittedModel = lme_bin, plot = T, re.form=NULL)  # pass
Anova(lme_bin)
```

## Fig 4G: Hit rate
```{r echo=TRUE, fig.height=6, fig.width=3, warning=FALSE}
graph_data = df

y_axis = seq(0, 100, 25)
p = ggplot(data=graph_data, aes(x=Treatment, y=Hit_rate, fill=Treatment, color=Treatment)) + 
  stat_summary(fun.data=boxplot_whiskers, geom="boxplot", na.rm = T, alpha=0.1, lwd=LINE_THICKNESS/6, fatten=1)+
  geom_line(aes(group = Subject, linetype=Hemisphere), color='black', alpha=0.1, size=LINE_THICKNESS/4) +
  ylab('Hit rate (%)') +
  xlab('') +
  scale_fill_manual(name = "Treatment",
                   values = treatment_colors) +
  scale_color_manual(name = "Treatment",
                   values = treatment_colors) +
    
  scale_y_continuous(breaks=y_axis, expand=c(0, 0)) +
  coord_cartesian(ylim = c(min(y_axis), max(y_axis))) +
    
  annotate("text", x=1.5, y=90, label='Saline', color=treatment_colors[1], size=5, hjust=0) + 
  annotate("text", x=1.5, y=86, label='Muscimol', color=treatment_colors[2], size=5, hjust=0) + 
    
  theme(
    legend.position = 'none',
    axis.title.x=element_blank(),
    axis.line.x = element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p
```

### Stats
```{r echo=TRUE}
lme_data = graph_data
lme_bin <- glmmTMB(Hit_rate~Treatment + (1 | Subject) , data=lme_data, family=gaussian)
simulationOutput <- simulateResiduals(fittedModel = lme_bin, plot = T, re.form=NULL)  # pass
Anova(lme_bin)
```

## Fig 4H: False alarm rate
```{r echo=TRUE, fig.height=6, fig.width=3, warning=FALSE}
graph_data = df

y_axis = seq(0, 100, 25)
p = ggplot(data=graph_data, aes(x=Treatment, y=FA_rate, fill=Treatment, color=Treatment)) + 
  stat_summary(fun.data=boxplot_whiskers, geom="boxplot", na.rm = T, alpha=0.1, lwd=LINE_THICKNESS/6, fatten=1)+
  geom_line(aes(group = Subject, linetype=Hemisphere), color='black', alpha=0.1, size=LINE_THICKNESS/4) +
  ylab('False alarm rate (%)') +
  xlab('') +
  scale_fill_manual(name = "Treatment",
                   values = treatment_colors) +
  scale_color_manual(name = "Treatment",
                   values = treatment_colors) +
    
  scale_y_continuous(breaks=y_axis, expand=c(0, 0)) +
  coord_cartesian(ylim = c(min(y_axis), max(y_axis))) +
    
  annotate("text", x=1.5, y=90, label='Saline', color=treatment_colors[1], size=5, hjust=0) + 
  annotate("text", x=1.5, y=86, label='Muscimol', color=treatment_colors[2], size=5, hjust=0) + 
    
  theme(
    legend.position = 'none',
    axis.title.x=element_blank(),
    axis.line.x = element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p
```

### Stats
```{r echo=TRUE}
lme_data = graph_data
lme_bin <- glmmTMB(FA_rate~Treatment + (1 | Subject) , data=lme_data, family=gaussian)
simulationOutput <- simulateResiduals(fittedModel = lme_bin, plot = T, re.form=NULL)  # pass
Anova(lme_bin)
```
# Fig S4: Miss rates explain lower trial completion and higher false alarm rates under OFC inactivation
## Fig S4A: Miss rates vs trial completion
```{r echo=TRUE, fig.height=6, fig.width=3, warning=FALSE}
graph_data = df
graph_data$Miss_rate = 100 - graph_data$Hit_rate

y_axis = seq(0, 10, 2)
x_axis = seq(0, 100, 25)
p =ggplot(data=graph_data, aes(x=Miss_rate, y=Trial_rate_per_min, fill=Treatment)) + 
  geom_point(size=LINE_THICKNESS*3,
             shape=21,
             color='NA',
             alpha=0.7) +
  geom_line(size=LINE_THICKNESS,
           color='black',
           alpha=0.1,
           aes(group=Subject, linetype=Hemisphere)) +
  stat_smooth(method = "lm", se = T,  alpha=0.1, size=LINE_THICKNESS, formula=y~x, color='black', fill='black') +
  # stat_cor(method = "spearman", r.digits = 2, p.accuracy = 0.001, size=LINE_THICKNESS*4, label.y=c(1, 1.5),
  #          output.type = 'text', aes(color=Treatment)) +
  scale_fill_manual(name = "Treatment", values = treatment_colors) +
  scale_color_manual(name = "Treatment",
                   values = treatment_colors) +
  ylab('AM trials / minute') + xlab('Miss rate (%)') +
  # coord_cartesian(ylim=c(-0.1, 3)) +
  annotate("text", x=5, y=1.5, label='Saline', color=treatment_colors[1], size=5, hjust=0) + 
  annotate("text", x=5, y=1.1, label='Muscimol', color=treatment_colors[2], size=5, hjust=0) + 
    
  scale_y_continuous(breaks=y_axis, expand=c(0, 0)) +
  scale_x_continuous(breaks=x_axis, expand=c(0, 0)) +
  coord_cartesian(ylim = c(min(y_axis), max(y_axis)),
                  xlim = c(min(x_axis), max(x_axis))) +
    
   theme(legend.position = "none",
         strip.text.x = element_blank())
p
```

### Stats
```{r echo=TRUE}
lme_data = graph_data
lme_bin <- glmmTMB(Trial_rate_per_min~Miss_rate + (1 | Subject) , data=lme_data, family=gaussian)
simulationOutput <- simulateResiduals(fittedModel = lme_bin, plot = T, re.form=NULL)  # pass
Anova(lme_bin)
```

## Fig S4B: Miss rates vs False alarm rates
```{r echo=TRUE, fig.height=6, fig.width=3, warning=FALSE}
graph_data = df
graph_data$Miss_rate = 100 - graph_data$Hit_rate

y_axis = seq(0, 20, 5)
x_axis = seq(0, 100, 25)
p =ggplot(data=graph_data, aes(x=Miss_rate, y=FA_rate, fill=Treatment)) + 
  geom_point(size=LINE_THICKNESS*3,
             shape=21,
             color='NA',
             alpha=0.7) +
  geom_line(size=LINE_THICKNESS,
           color='black',
           alpha=0.1,
           aes(group=Subject, linetype=Hemisphere)) +
  stat_smooth(method = "lm", se = T,  alpha=0.1, size=LINE_THICKNESS, formula=y~x, color='black', fill='black') +
  scale_fill_manual(name = "Treatment", values = treatment_colors) +
  scale_color_manual(name = "Treatment",
                   values = treatment_colors) +
  ylab('False alarm rate (%)') + xlab('Miss rate (%)') +
  # coord_cartesian(ylim=c(-0.1, 3)) +
  annotate("text", x=5, y=18, label='Saline', color=treatment_colors[1], size=5, hjust=0) + 
  annotate("text", x=5, y=17, label='Muscimol', color=treatment_colors[2], size=5, hjust=0) + 
    
  scale_y_continuous(breaks=y_axis, expand=c(0, 0)) +
  scale_x_continuous(breaks=x_axis, expand=c(0, 0)) +
  coord_cartesian(ylim = c(min(y_axis)-2.5, max(y_axis)),
                  xlim = c(min(x_axis), max(x_axis))) +
    
   theme(legend.position = "none",
         strip.text.x = element_blank())
p
```

### Stats
```{r echo=TRUE}
lme_data = graph_data
lme_bin <- glmmTMB(FA_rate~Miss_rate + (1 | Subject) , data=lme_data, family=gaussian)
simulationOutput <- simulateResiduals(fittedModel = lme_bin, plot = T, re.form=NULL)  # pass
Anova(lme_bin)
```
