---
title: "OFC recordings - Analyses"
editor_options:
  chunk_output_type: inline
chunk_output_type: console
---

# Load libraries and data from preprocessing pipeline
## Load previously exported environment. 
Uncomment chunk below if the second block of code has been run previously and does not need modifications
```{r echo=TRUE}

# 
# load('./Data/OFC_ephys_analyses_env.RData')
# 
# library(ggplot2)
# library(dplyr)
# library(tidyr)
# # install.packages(c('remotes', 'TMB'))
# # remotes::install_github("glmmTMB/glmmTMB/glmmTMB", build_vignettes=FALSE)
# library(glmmTMB)
# library(DHARMa)
# library(car)
# library(reshape2)
# library(emmeans)
# library(rcompanion)
# # Create the notin operator
# `%notin%` <- Negate(`%in%`)
# 
# # Some global plot parameters if modification is needed.
# source('./r_theme.r', echo=F)
# theme_set(theme_mml(base_size = 20))
# LINE_THICKNESS = 1
# ERRORBAR_THICKNESS = LINE_THICKNESS/2
# INDIVIDUAL_DATAPOINT_LINE = LINE_THICKNESS/1.5
# SMALL_PLOTS_LINE_THICKNESS = LINE_THICKNESS/3
# ACTIVEBASELINE_MODULATION_COLORS = c('#E39D51','#356B83', 'gray')  # task-suppressed, -enhanced, -unchanged
# 
# TRIALTYPE_MODULATION_COLORS = c('#46BDD7', '#9E4770', '#EB172C', 'black')  # Hit, FA, miss, passive

```

## Process 
```{r echo=TRUE}
library(ggplot2)
library(dplyr)
library(tidyr)
# install.packages(c('remotes', 'TMB'))
# remotes::install_github("glmmTMB/glmmTMB/glmmTMB", build_vignettes=FALSE)
library(glmmTMB)
library(DHARMa)
library(car)
library(reshape2)
library(emmeans)
library(rcompanion)
# Create the notin operator
`%notin%` <- Negate(`%in%`)

# Some global plot parameters if modification is needed.
source('./r_theme.r', echo=F)
theme_set(theme_mml(base_size = 20))
LINE_THICKNESS = 1
ERRORBAR_THICKNESS = LINE_THICKNESS/2
INDIVIDUAL_DATAPOINT_LINE = LINE_THICKNESS/1.5
SMALL_PLOTS_LINE_THICKNESS = LINE_THICKNESS/3
ACTIVEBASELINE_MODULATION_COLORS = c('#E39D51','#356B83', 'gray')  # task-suppressed, -enhanced, -unchanged

TRIALTYPE_MODULATION_COLORS = c('#46BDD7', '#9E4770', '#EB172C', 'black')  # Hit, FA, miss, passive

boxplot_whiskers <- function(x) {
  r <- quantile(x, probs = c(0.10, 0.25, 0.5, 0.75, 0.90))
  names(r) <- c("ymin", "lower", "middle", "upper", "ymax")
  r
}

# Custom functions
z_score = function(response_df, baseline_df) {
  
  # If variables have equal length, assume covariates, else don't use cov()
  if(length(response_df) == length(baseline_df)) {
    return(
      (mean(response_df) - mean(baseline_df)) / 
        (sqrt(var(response_df) + var(baseline_df) - 
        2*cov(response_df, baseline_df)))
    )
  } else {
    return(
      (mean(response_df) - mean(baseline_df)) / 
        (sqrt(var(response_df) + var(baseline_df)))
    )
  }
}

zeromin = function(x) {
  return( (x + 2*abs(min(x))) )
}

# Load data from preprocessing pipeline
df = read.csv('./Data/OFCPL_allTrial_df.csv')

# Remove eventual NA rows
df[df == "NaN"]<-NA
df = df[!is.na(df$Subject),]


# Factorize some columns
df$Session = factor(df$Session, levels=c('Pre', 'Active', 'Post', 'Post1h'))
cols_to_factorize = c('Unit', 'Subject', 'Date', 'TrialID', 'AMdepth', 'Period', 'Subject_date', 'Cluster_quality_MML', 'Cluster_quality_Allen', 'First_am_above_threshold_flag', 'AM_above_threshold_flag', 'AMThreshold_modulated', 'AMThreshold_modulation_direction')
df[cols_to_factorize] <- lapply(df[cols_to_factorize], factor) 

# Separate SU and MU activity
# Call 'good' the intersection between MML and Allen classification
df$Cluster_quality = 'mua'
df[df$Cluster_quality_MML == 'good' & df$Cluster_quality_Allen == 'good',]$Cluster_quality = 'good'

# Simplify trial outcome labels
df$Trial_type = 'Miss (no shock)'
df[df$Hit == 1,]$Trial_type = 'Hit'
df[df$Miss == 1 & df$ShockFlag == 1,]$Trial_type = 'Miss (shock)'
df[df$FA == 1,]$Trial_type = 'False alarm'

df$Trial_type = factor(df$Trial_type, levels=c('Miss (shock)', 'Hit', 'False alarm', 'Miss (no shock)'))

# Load behavioral files
threshold_df = read.csv('./Data/OFCPL_behavior_df.csv')

# Elliminate eventual subjects not in behavioral threshold_df
df = df[df$Subject %in% unique(threshold_df$Subject),]

df$Cluster_quality_Allen = 'mua'
df[(df$ISI_FPRate < 0.5) & (df$Fraction_missing < 0.1) & (df$Presence_ratio > 0.9) & (df$ISI_ViolationRate < 2),]$Cluster_quality_Allen = 'good'

# Call 'good' the intersection between MML and Allen 
df$Cluster_quality = 'mua'
df[df$Cluster_quality_MML == 'good' & df$Cluster_quality_Allen == 'good',]$Cluster_quality = 'good'

# ---------------------------------------------------------------------------
# Data curation
# Ensure  subjects 232 and 270 are not here (insufficient training days and units, respectively)
# Also SUBJ-ID-197 anatomy was off; probably only in OFC towards the end of training
subjects_to_exclude = c('SUBJ-ID-232', 'SUBJ-ID-270', 'SUBJ-ID-197')
df = df[df$Subject %notin% subjects_to_exclude,]

# SUBJ-ID-390_2022-06-24_16-37-06_PassivePost 
# eliminate trials between 108.5 and 171.1 s when animal unplugged SPI cable; these translate to trials 77 through 119
df = df[!(df$Key_file == 'SUBJ-ID-390_SUBJ-ID-390_2022-06-24_16-37-06_PassivePost_trialInfo' & df$TrialID %in% 77:119),]

# Something strange happened on SUBJ-ID-390 6/27/22 Active where DACs become out of sync with ePsych by a variable offset starting when the animal regressed in AM depth difficulty after AM trial 7 (TrialID 178 on); remove trials after that here
# This did not happen in any other session
df = df[!(df$Key_file == 'SUBJ-ID-390_SUBJ-ID-390_2022-06-27_18-11-15_Active_trialInfo' & as.numeric(as.character(df$TrialID)) > 177),]

# Remove units without Pre recording
pre_units = unique(df[df$Session == 'Pre',]$Unit)
df = df[df$Unit %in% pre_units,]
df = droplevels(df)
# ---------------------------------------------------------------------------

# Save image for faster loading
save.image('./Data/OFC_ephys_analyses_env.RData')

# Some garbage collection
gc()
```

# Get some descriptives
```{r echo=TRUE}
# Training days per subject
df %>% group_by(Subject) %>%
  summarise(
    Max_day = max(Day_of_training)
  )

# How many trials per session?
df_info = df[df$AMdepth_db != -40 & df$Period == 'Baseline',] %>% group_by(Subject, Session, Subject_date) %>%
  summarise(
    Trial_count = length(unique(TrialID))
  )
df_info %>% group_by(Session) %>%
  summarise(
    Trial_count_mean = mean(Trial_count),
    Trial_count_ste = sd(Trial_count)/sqrt(n() - 1)
  )

# How many single units?
df_info = df[df$AMdepth_db != -40 & df$Period == 'Baseline',] %>% group_by(Subject, Unit, Subject_date, Cluster_quality, ActiveTrial_modulation_direction) %>%
  summarise(
    Trial_count = length(unique(TrialID)),
    ISI_FPRate = mean(ISI_FPRate),
    ISI_ViolationRate = mean(ISI_ViolationRate),
    Fraction_missing = mean(Fraction_missing)
  )
table(df_info$Cluster_quality)

```


# Figure 2E-G: Task-dependent tonic modulation
## Fig 2E: Modulation strength distribution 
```{r echo=TRUE, fig.height=12, fig.width=12, warning=FALSE}
# Prepare data using relevant variables
df_grouped = df[df$Trial_type != 'False alarm' & df$Period == 'Baseline',] %>% group_by(Unit, Subject, Date, Day_of_training, ActiveBaseline_modulation_direction) %>%
  summarise( 
    FR_Hz_baseline = mean(FR_Hz),
    Zscore_taskPassive = z_score(FR_Hz[Session=='Active'], FR_Hz[Session=='Pre'])
  )
df_grouped$ActiveBaseline_modulation_direction = factor(df_grouped$ActiveBaseline_modulation_direction, levels=c('decrease', 'increase', 'none'))

# Plot
graph_data = df_grouped[!is.nan(df_grouped$Zscore_taskPassive),]
graph_data = graph_data[order(graph_data$Zscore_taskPassive),]
graph_data$Plot_order = seq(1, nrow(graph_data))

y_axis = seq(-2, 6, 2)
p = ggplot(data=graph_data, aes(x = Plot_order, y = Zscore_taskPassive, fill=ActiveBaseline_modulation_direction)) + 
  geom_bar(stat='identity', width=1) +
  scale_fill_manual(values=ACTIVEBASELINE_MODULATION_COLORS, name='',
                    labels=c('Task-\nsuppressed', 'Task-\nenhanced', 'Task-\nunchanged')) +
  geom_hline(yintercept = 0, color='black', linetype="dashed") +

  ylab('Context modulation (z-score)') +
  
  scale_y_continuous(breaks=y_axis, expand=c(0, 0)) +
  coord_cartesian(ylim = c(min(y_axis), max(y_axis))) +
  
  theme(
    strip.background = element_blank(),
    strip.text.y = element_blank(),
    legend.position = c(0.2, 0.85),
    axis.title.x=element_blank(),
    axis.text.x=element_blank(),
    axis.ticks.x=element_blank()
  ) +
  guides(x = "none")
p
```


## Fig 2F: Modulation strength comparison among groups
```{r echo=TRUE, fig.height=12, fig.width=12, warning=FALSE}
# Prepare data using relevant variables
df_grouped = df[df$Trial_type != 'False alarm' & df$Period == 'Baseline',] %>% group_by(Unit, Subject, Date, Day_of_training, ActiveBaseline_modulation_direction) %>%
  summarise( 
    FR_Hz_baseline = mean(FR_Hz),
    Zscore_taskPassive = z_score(FR_Hz[Session=='Active'], FR_Hz[Session=='Pre'])
  )
df_grouped$ActiveBaseline_modulation_direction = factor(df_grouped$ActiveBaseline_modulation_direction, levels=c('decrease', 'increase', 'none'))

# Plot
graph_data = df_grouped[!is.nan(df_grouped$Zscore_taskPassive),]
# reversed_colors = rev(ACTIVEBASELINE_MODULATION_COLORS[1:2])
y_axis = seq(0, 1.5, 0.5)
p = ggplot(data=graph_data, aes(x = ActiveBaseline_modulation_direction, y = abs(Zscore_taskPassive), fill=ActiveBaseline_modulation_direction, color=ActiveBaseline_modulation_direction)) + 
  stat_summary(fun.data=boxplot_whiskers, geom="boxplot", na.rm = T, alpha=0.3, lwd=LINE_THICKNESS/2, fatten=1, width=0.75)+
  
  ylab(expression('|Context modulation|')) +
  
  scale_fill_manual(values=ACTIVEBASELINE_MODULATION_COLORS, name='',
                    guide='none') +
  
  scale_color_manual(values=ACTIVEBASELINE_MODULATION_COLORS, 
                     labels=c('Task-\nsuppressed', 'Task-\nenhanced', 'Task-\nunchanged'), name='') +
  
  scale_y_continuous(breaks=y_axis, expand=c(0, 0)) +
  coord_cartesian(ylim = c(min(y_axis), max(y_axis))) +

  theme(
    legend.position = c(0.2, 0.85),
    axis.title.x=element_blank(),
    axis.line.x = element_blank(),
    axis.text.x=element_blank(),
    axis.ticks.x=element_blank()
  )
p
```
### Stats
```{r echo=TRUE}
lme_data = graph_data
lme_bin <- glmmTMB(sqrt(sqrt(abs(Zscore_taskPassive))) ~ ActiveBaseline_modulation_direction + (1 | Subject/Unit),  data=lme_data, family=gaussian)
simulationOutput <- simulateResiduals(fittedModel = lme_bin, plot = T, re.form=NULL)  # pass
Anova(lme_bin)
pairs(regrid(emmeans(lme_bin,  ~ActiveBaseline_modulation_direction)),  adjust='Bonferroni')
```

## Fig 2G: Task-dependent firing rate change 
```{r echo=TRUE, fig.height=10, fig.width=15, warning=FALSE}
# Group data using relevant columns
df_grouped = df[df$Trial_type != 'False alarm',] %>% group_by(Unit, Subject, Subject_date, Session, Period, ActiveBaseline_modulated, ActiveBaseline_modulation_direction, Cluster_quality) %>%
  summarise( 
    FR_Hz = mean(FR_Hz, na.rm=T),
    Spike_count = round(mean(Spike_count, na.rm=T)),
    Threshold_improvement = mean(Threshold_improvement, na.rm=T),
    Threshold_improvement_linear = mean(Threshold_improvement_linear, na.rm=T),
    Threshold_linear = mean(Threshold_linear, na.rm=T),
    Threshold = mean(Threshold, na.rm=T)
  )
df_grouped$ActiveBaseline_modulation_direction = factor(df_grouped$ActiveBaseline_modulation_direction, levels=c('decrease', 'increase', 'none'))
df_grouped$Session = factor(df_grouped$Session, levels=c('Pre', 'Active', 'Post'))
df_grouped = df_grouped[!is.na(df_grouped$Session),]

# Plot
graph_data =  df_grouped[df_grouped$Period=='Baseline',]

graph_data$ActiveBaseline_modulation_direction = factor(graph_data$ActiveBaseline_modulation_direction, levels=c('decrease', 'increase', 'none'))
y_axis = seq(0, 30, 10)
p =ggplot(data=graph_data, aes(x=Session, y=(FR_Hz), fill=ActiveBaseline_modulation_direction, color=ActiveBaseline_modulation_direction)) + 
  facet_grid(.~ActiveBaseline_modulation_direction) +

  stat_summary(fun.data=boxplot_whiskers, geom="boxplot", na.rm = T, alpha=0.3, lwd=LINE_THICKNESS/2, fatten=1, width=0.75)+
  
  ylab('Firing rate (Hz)') +
    scale_x_discrete(labels=c("Pre" = "Pre", "Active" = "Task",
                                "Post" = "Post")) +
  scale_fill_manual(values=ACTIVEBASELINE_MODULATION_COLORS, name='',
                    guide='none') +
  
  scale_color_manual(values=ACTIVEBASELINE_MODULATION_COLORS, 
                     labels=c('Task-\nsuppressed', 'Task-\nenhanced', 'Task-\nunchanged'), name='') +
  
  scale_y_continuous(breaks=y_axis, expand=c(0, 0)) +
  coord_cartesian(ylim = c(min(y_axis), max(y_axis))) +

  theme(
    strip.background = element_blank(),
    strip.text.y = element_blank(),
    strip.text.x = element_blank(),
    axis.title.x = element_blank(),
    axis.line.x = element_blank(),
    axis.ticks.x=element_blank(),
    legend.position = c(0.2, 0.85),
    axis.text.x = element_text(angle = 270, vjust = 0.5, hjust=0)
  ) 
p

```

### Stats
```{r echo=TRUE}
lme_data = graph_data[graph_data$ActiveBaseline_modulation_direction == 'decrease',]
lme_bin <- glmmTMB(sqrt(FR_Hz)~Session + (1 | Subject/Unit/Session), data=lme_data, family=gaussian)
simulationOutput <- simulateResiduals(fittedModel = lme_bin, plot = T, re.form=NULL)  # pass
Anova(lme_bin)
pairs(regrid(emmeans(lme_bin,  ~Session)),  adjust='Bonferroni')

lme_data = graph_data[graph_data$ActiveBaseline_modulation_direction == 'increase',]
lme_bin <- glmmTMB(sqrt((FR_Hz))/100~Session + (1 | Subject/Unit/Session), data=lme_data, family=gaussian)
simulationOutput <- simulateResiduals(fittedModel = lme_bin, plot = T, re.form=NULL)  # pass
Anova(lme_bin)
pairs(regrid(emmeans(lme_bin,  ~Session)),  adjust='Bonferroni')


lme_data = graph_data[graph_data$ActiveBaseline_modulation_direction == 'none',]
lme_bin <- glmmTMB((sqrt(FR_Hz))~Session + (1 | Subject/Unit/Session), data=lme_data, family=gaussian)
simulationOutput <- simulateResiduals(fittedModel = lme_bin, plot = T, re.form=NULL)  # pass
Anova(lme_bin)

```


# Fig 3B-C: Pre-spout withdrawal
Analyze auROC data extracted from the Python pipeline
## Fig 3B
```{r echo=TRUE, fig.height=10, fig.width=15, warning=FALSE}
auroc_df = read.csv('./Data/TrialType_preSpoutOffset_allUnitsauROC_plotData.csv')
auroc_df = separate(data = auroc_df, col = Unit,  sep = "_", into=c("Subject", "Date", "temp1"), remove=F)
# Remove temp columns
auroc_df = auroc_df[, -grep("temp", colnames(auroc_df))]

time_slice = c(-0.5, 0)  # 0-0.1 s is not included

auroc_cutoffs = c(0.45, 0.55)

df_grouped = auroc_df[auroc_df$TrialType != 'SpoutOff_misses_auroc',] %>% group_by(Unit, Subject, TrialType, ActiveBaseline_modulation_direction) %>%
  summarise( 
    auroc_timeSlice_mean = mean(auROC[(Time_s >= time_slice[1]) & (Time_s < time_slice[2])], na.rm=T),
    auroc_timeSlice_abs = mean(abs(auROC[(Time_s >= time_slice[1]) & (Time_s < time_slice[2])] - 0.5), na.rm=T),
    auroc_timeSlice_all = all( abs(auROC[(Time_s >= time_slice[1]) & (Time_s < time_slice[2])] - 0.5) > 0.1)
  )
df_grouped = df_grouped[!is.na(df_grouped$auroc_timeSlice_mean),]
df_grouped$TrialType = factor(df_grouped$TrialType, levels=c('SpoutOff_hits_auroc', 'SpoutOff_FAs_auroc'))
levels(df_grouped$TrialType) = c('Hit', 'False alarm')


# Cutoff based on auROC
df_grouped$PreHit_modulated = 'unmodulated'
df_grouped$PreFA_modulated = 'unmodulated'
df_grouped$PreMiss_modulated = 'unmodulated'
df_grouped$PreHitOrFA_modulated = 'unmodulated'

df_grouped$PreHit_modulation_direction = 'none'
df_grouped$PreFA_modulation_direction = 'none'
df_grouped$PreMiss_modulation_direction = 'none'

# Hit-modulated
temp_df = df_grouped[df_grouped$TrialType == 'Hit',]
temp_increase_units = temp_df[(temp_df$auroc_timeSlice_mean > auroc_cutoffs[2]),]$Unit
temp_decrease_units = temp_df[(temp_df$auroc_timeSlice_mean < auroc_cutoffs[1]),]$Unit
df_grouped[df_grouped$Unit %in% temp_increase_units,]$PreHit_modulation_direction = 'increase'
df_grouped[df_grouped$Unit %in% temp_decrease_units,]$PreHit_modulation_direction = 'decrease'
df_grouped[df_grouped$PreHit_modulation_direction != 'none',]$PreHit_modulated = 'modulated'

# FA-modulated
temp_df = df_grouped[df_grouped$TrialType == 'False alarm',]
temp_increase_units = temp_df[(temp_df$auroc_timeSlice_mean > auroc_cutoffs[2]),]$Unit
temp_decrease_units = temp_df[(temp_df$auroc_timeSlice_mean < auroc_cutoffs[1]),]$Unit
df_grouped[df_grouped$Unit %in% temp_increase_units,]$PreFA_modulation_direction = 'increase'
df_grouped[df_grouped$Unit %in% temp_decrease_units,]$PreFA_modulation_direction = 'decrease'
df_grouped[df_grouped$PreFA_modulation_direction != 'none',]$PreFA_modulated = 'modulated'

# Either hit or FA modulated
df_grouped[(df_grouped$PreHit_modulated == 'modulated') | (df_grouped$PreFA_modulated == 'modulated'),]$PreHitOrFA_modulated = 'modulated' 

# Get proportions
graph_data =  df_grouped[df_grouped$TrialType=='Hit',]

cur_table = table(graph_data$PreHit_modulation_direction)
cur_table
cur_table/sum(cur_table)
hit_values = cur_table[1:2]/sum(cur_table)*100

cur_table = table(graph_data$PreFA_modulation_direction)
cur_table
cur_table/sum(cur_table)
fa_values = cur_table[1:2]/sum(cur_table)*100

cur_table = table(graph_data$PreHitOrFA_modulated)
cur_table
cur_table/sum(cur_table)

# Plot distributions
graph_data = df_grouped

y_axis = seq(0, 40, 20)
x_axis = c(0, 0.45, 0.55, 1)
p = ggplot(df_grouped, aes(x=auroc_timeSlice_mean, fill=TrialType)) + 

  geom_histogram(alpha=0.5, position="identity", binwidth=0.01, color='NA', boundary=0) +
  
  geom_vline(xintercept=0.55, size=LINE_THICKNESS/4) +
  
  geom_vline(xintercept=0.45, size=LINE_THICKNESS/4) +
  
  scale_y_continuous(breaks=y_axis, expand=c(0, 0)) +
  
  scale_x_continuous(breaks=x_axis, expand=c(0, 0)) +
  
  coord_cartesian(ylim = c(min(y_axis), max(y_axis)), 
                  xlim = c(min(x_axis), max(x_axis))) +
  
  scale_color_manual(values = TRIALTYPE_MODULATION_COLORS, name='') +
  scale_fill_manual(values = TRIALTYPE_MODULATION_COLORS, name='') +
  
  ylab('Number of units') +
  xlab('Phasic modulation') +
  
  # Add percentage values
  annotate("text", x=c(0.2, 0.8), y=c(20, 20), label=paste(round(hit_values, 0), '%', sep=''), color=TRIALTYPE_MODULATION_COLORS[1]) + 
  annotate("text", x=c(0.2, 0.8), y=c(18, 18), label=paste(round(fa_values, 0), '%', sep=''), color=TRIALTYPE_MODULATION_COLORS[2]) + 
  
  theme(
    legend.position=c(0.85, 0.85)
  )
p
```

## Fig 3C
```{r echo=TRUE, fig.height=10, fig.width=15, warning=FALSE}
graph_data = auroc_df[(auroc_df$Time_s >= -1) & (auroc_df$Time_s < 0) & auroc_df$TrialType != 'SpoutOff_misses_auroc',]
graph_data = graph_data[!is.na(graph_data$auROC),]
graph_data$TrialType = factor(graph_data$TrialType, levels=c('SpoutOff_hits_auroc', 'SpoutOff_FAs_auroc'))
levels(graph_data$TrialType) = c('Hit', 'False alarm')

y_axis = seq(0.07, 0.17, 0.05)
x_axis = seq(-1, 0, 0.5)
p =ggplot(data=graph_data, aes(x=Time_s, y=abs(auROC-0.5), fill=TrialType, color=TrialType)) + 
  stat_summary(fun.data = mean_se, geom = "ribbon", na.rm = T, size=ERRORBAR_THICKNESS/2, width=ERRORBAR_THICKNESS/2, alpha=0.3, color=NA) +
  stat_summary(fun="mean", geom="line", na.rm = T, alpha = 1, size=LINE_THICKNESS/4) +
  
  ylab('Phasic modulation') +
  xlab('Time re: spout withdrawal (s)') +
  
  scale_y_continuous(breaks=y_axis, expand=c(0, 0)) +
  
  scale_x_continuous(breaks=x_axis, expand=c(0, 0)) +
  
  coord_cartesian(ylim = c(min(y_axis), max(y_axis)), 
                  xlim = c(min(x_axis), max(x_axis))) +

  scale_color_manual(values = TRIALTYPE_MODULATION_COLORS, name='') +
  scale_fill_manual(values = TRIALTYPE_MODULATION_COLORS, name='') +
  
  theme(
    strip.background = element_blank(),
    strip.text.y = element_blank(),
    strip.text.x = element_blank(),
    legend.position = c(0.25, 0.85),
    panel.spacing = unit(1, "lines")
  )

p

```

### Stats
```{r echo=TRUE}
lme_data = df_grouped
lme_bin <- glmmTMB((blom(auroc_timeSlice_abs, method='rankit'))~ TrialType + (1 | Subject/Unit/TrialType),  data=lme_data, family=gaussian)
simulationOutput <- simulateResiduals(fittedModel = lme_bin, plot = T, re.form=NULL)  # pass
Anova(lme_bin)
```

# Fig S2: Post-spout withdrawal
## Fig S2B
```{r echo=TRUE, fig.height=10, fig.width=15, warning=FALSE}
auroc_df = read.csv('./Data/TrialType_postSpoutOffset_allUnitsauROC_plotData.csv')
auroc_df = separate(data = auroc_df, col = Unit,  sep = "_", into=c("Subject", "Date", "temp1"), remove=F)
auroc_df = auroc_df[, -grep("temp", colnames(auroc_df))]  # Remove temp columns

time_slice = c(0.3, 0.8) # 0.8-0.9 s is not included

auroc_cutoffs = c(0.45, 0.55)

df_grouped = auroc_df[auroc_df$TrialType %in% c('SpoutOff_hits_auroc', 'SpoutOff_FAs_auroc', 'SpoutOff_misses_auroc'),] %>% group_by(Unit, Subject, TrialType, ActiveBaseline_modulation_direction) %>%
  summarise( 
    auroc_timeSlice_mean = mean(auROC[(Time_s >= time_slice[1]) & (Time_s < time_slice[2])], na.rm=T),
    auroc_timeSlice_abs = mean(abs(auROC[(Time_s >= time_slice[1]) & (Time_s < time_slice[2])] - 0.5), na.rm=T),
    auroc_timeSlice_all = all( abs(auROC[(Time_s >= time_slice[1]) & (Time_s < time_slice[2])] - 0.5) >= 0.1)
  )
df_grouped = df_grouped[!is.na(df_grouped$auroc_timeSlice_mean),]
df_grouped$TrialType = factor(df_grouped$TrialType, levels=c('SpoutOff_hits_auroc', 'SpoutOff_FAs_auroc', 'SpoutOff_misses_auroc'))
levels(df_grouped$TrialType) = c('Hit', 'False alarm', 'Miss')


# Cutoff based on auROC
df_grouped$PostHit_modulated = 'unmodulated'
df_grouped$PostFA_modulated = 'unmodulated'
df_grouped$PostMiss_modulated = 'unmodulated'
df_grouped$PostHitOrFAOrMiss_modulated = 'unmodulated'

df_grouped$PostHit_modulation_direction = 'none'
df_grouped$PostFA_modulation_direction = 'none'
df_grouped$PostMiss_modulation_direction = 'none'

# Hit modulation
temp_df = df_grouped[df_grouped$TrialType == 'Hit',]
temp_increase_units = temp_df[(temp_df$auroc_timeSlice_mean > auroc_cutoffs[2]),]$Unit
temp_decrease_units = temp_df[(temp_df$auroc_timeSlice_mean < auroc_cutoffs[1]),]$Unit
df_grouped[df_grouped$Unit %in% temp_increase_units,]$PostHit_modulation_direction = 'increase'
df_grouped[df_grouped$Unit %in% temp_decrease_units,]$PostHit_modulation_direction = 'decrease'
df_grouped[df_grouped$PostHit_modulation_direction != 'none',]$PostHit_modulated = 'modulated'

# FA modulation
temp_df = df_grouped[df_grouped$TrialType == 'False alarm',]
temp_increase_units = temp_df[(temp_df$auroc_timeSlice_mean > auroc_cutoffs[2]),]$Unit
temp_decrease_units = temp_df[(temp_df$auroc_timeSlice_mean < auroc_cutoffs[1]),]$Unit
df_grouped[df_grouped$Unit %in% temp_increase_units,]$PostFA_modulation_direction = 'increase'
df_grouped[df_grouped$Unit %in% temp_decrease_units,]$PostFA_modulation_direction = 'decrease'
df_grouped[df_grouped$PostFA_modulation_direction != 'none',]$PostFA_modulated = 'modulated'

# Miss modulation
temp_df = df_grouped[df_grouped$TrialType == 'Miss',]
temp_increase_units = temp_df[(temp_df$auroc_timeSlice_mean > auroc_cutoffs[2]),]$Unit
temp_decrease_units = temp_df[(temp_df$auroc_timeSlice_mean < auroc_cutoffs[1]),]$Unit
df_grouped[df_grouped$Unit %in% temp_increase_units,]$PostMiss_modulation_direction = 'increase'
df_grouped[df_grouped$Unit %in% temp_decrease_units,]$PostMiss_modulation_direction = 'decrease'
df_grouped[df_grouped$PostMiss_modulation_direction != 'none',]$PostMiss_modulated = 'modulated'

# Either hit, FA or miss modulated
df_grouped[(df_grouped$PostHit_modulated == 'modulated') | (df_grouped$PostFA_modulated == 'modulated'),]$PostHitOrFAOrMiss_modulated = 'modulated' 


# Get proportions
graph_data =  df_grouped[df_grouped$TrialType=='Hit',]

cur_table = table(graph_data$PostHit_modulation_direction)
cur_table
cur_table/sum(cur_table)
hit_values = cur_table[1:2]/sum(cur_table)*100

cur_table = table(graph_data$PostFA_modulation_direction)
cur_table
cur_table/sum(cur_table)
fa_values = cur_table[1:2]/sum(cur_table)*100

cur_table = table(graph_data$PostMiss_modulation_direction)
cur_table
cur_table/sum(cur_table)
miss_values = cur_table[1:2]/sum(cur_table)*100

cur_table = table(graph_data$PostHitOrFAOrMiss_modulated)
cur_table
cur_table/sum(cur_table)

# Plot distributions
graph_data = df_grouped

y_axis = seq(0, 40, 20)
x_axis = c(0, 0.45, 0.55, 1)
p = ggplot(df_grouped, aes(x=auroc_timeSlice_mean, fill=TrialType)) + 
  # facet_grid(.~TrialType) +
    # geom_density(alpha=0.2, fill='NA', adjust=1, size=LINE_THICKNESS/2) +

  

  geom_histogram(alpha=0.5, position="identity", binwidth=0.01, color='NA', boundary=0) +
  
  geom_vline(xintercept=0.55, size=LINE_THICKNESS/4) +
  
  geom_vline(xintercept=0.45, size=LINE_THICKNESS/4) +
  
  scale_y_continuous(breaks=y_axis, expand=c(0, 0)) +
  
  scale_x_continuous(breaks=x_axis, expand=c(0, 0)) +
  
  coord_cartesian(ylim = c(min(y_axis), max(y_axis)), 
                  xlim = c(min(x_axis), max(x_axis))) +

  # scale_linetype_manual(values = plot_linetypes) +
  scale_color_manual(values = TRIALTYPE_MODULATION_COLORS, name='') +
  scale_fill_manual(values = TRIALTYPE_MODULATION_COLORS, name='') +
  
  ylab('Number of units') +
  xlab('Phasic modulation') +
  
  # Add percentage values
  annotate("text", x=c(0.2, 0.8), y=c(20, 20), label=paste(round(hit_values, 0), '%', sep=''), color=TRIALTYPE_MODULATION_COLORS[1]) + 
  annotate("text", x=c(0.2, 0.8), y=c(18, 18), label=paste(round(fa_values, 0), '%', sep=''), color=TRIALTYPE_MODULATION_COLORS[2]) + 
  annotate("text", x=c(0.2, 0.8), y=c(16, 16), label=paste(round(miss_values, 0), '%', sep=''), color=TRIALTYPE_MODULATION_COLORS[3]) + 
  
  theme(
    legend.position = c(0.85, 0.85)
  )
p
```

## Fig S2C
```{r echo=TRUE, fig.height=10, fig.width=15, warning=FALSE}
graph_data =  df_grouped
# Plot the curves
graph_data = auroc_df[(auroc_df$Time_s >= 0.3) & (auroc_df$Time_s < 2),]
graph_data = graph_data[!is.na(graph_data$auROC),]
graph_data$TrialType = factor(graph_data$TrialType, levels=c('SpoutOff_hits_auroc', 'SpoutOff_FAs_auroc', 'SpoutOff_misses_auroc'))
levels(graph_data$TrialType) = c('Hit', 'False alarm', 'Miss')

y_axis = seq(0, 0.3, 0.1)
x_axis = c(0.3, 0.8, 1.5, 2)
p =ggplot(data=graph_data, aes(x=Time_s, y=abs(auROC-0.5), color=TrialType, fill=TrialType)) + 
  # facet_grid(.~PostHitOrFAOrMiss_modulated) +
  stat_summary(fun.data = mean_se, geom = "ribbon", na.rm = T, size=ERRORBAR_THICKNESS/2,  alpha=0.3, color=NA) +
  stat_summary(fun="mean", geom="line", na.rm = T, alpha = 1, size=LINE_THICKNESS/4) +
  
  ylab('Phasic modulation') +
  xlab('Time re: spout withdrawal (s)') +
  
  scale_y_continuous(breaks=y_axis, expand=c(0, 0)) +
  
  scale_x_continuous(breaks=x_axis, expand=c(0, 0)) +
  
  coord_cartesian(ylim = c(min(y_axis), max(y_axis)), 
                  xlim = c(min(x_axis), max(x_axis))) +
  
  scale_color_manual(values = TRIALTYPE_MODULATION_COLORS, name='') +
  scale_fill_manual(values = TRIALTYPE_MODULATION_COLORS, name='') +
  
  theme(
    strip.background = element_blank(),
    strip.text.y = element_blank(),
    strip.text.x = element_blank(),
    legend.position = c(0.85, 0.85),
    panel.spacing = unit(1, "lines")
  )

p
```

### Stats
```{r echo=TRUE}

lme_data = df_grouped
lme_bin <- glmmTMB(blom(auroc_timeSlice_abs, method='rankit')*10~ TrialType + (1 | Subject/Unit/TrialType),  data=lme_data, family=gaussian)
simulationOutput <- simulateResiduals(fittedModel = lme_bin, plot = T, re.form=NULL)  # pass
Anova(lme_bin)
pairs(regrid(emmeans(lme_bin,  ~TrialType)),  adjust='Bonferroni')

```

# Fig S3: Phasic firing by tonic modulation
## Fig S3B
```{r echo=TRUE, fig.height=10, fig.width=15, warning=FALSE}
auroc_df = read.csv('./Data/TrialType_postSpoutOffset_allUnitsauROC_plotData.csv')
auroc_df = separate(data = auroc_df, col = Unit,  sep = "_", into=c("Subject", "Date", "temp1"), remove=F)
# Remove temp columns
auroc_df = auroc_df[, -grep("temp", colnames(auroc_df))]

# Plot the curves
graph_data = auroc_df[(auroc_df$Time_s >= 0.3) & (auroc_df$Time_s < 2),]
graph_data = graph_data[!is.na(graph_data$auROC),]
graph_data$TrialType = factor(graph_data$TrialType, levels=c('SpoutOff_hits_auroc', 'SpoutOff_FAs_auroc', 'SpoutOff_misses_auroc'))
levels(graph_data$TrialType) = c('Hit', 'False alarm', 'Miss')

graph_data$ActiveBaseline_modulation_direction = factor(graph_data$ActiveBaseline_modulation_direction, levels=c('decrease', 'increase', 'none'))
levels(graph_data$ActiveBaseline_modulation_direction) = c('Task-suppressed', 'Task-enhanced', 'Task-unchanged')

y_axis = c(0, 0.1, 0.2, 0.3)
x_axis = c(0.3, 0.8, 1.5, 2)
p =ggplot(data=graph_data, aes(x=Time_s, y=abs(auROC-0.5), color=TrialType, fill=TrialType)) + 
  facet_grid(.~ActiveBaseline_modulation_direction) +
  stat_summary(fun.data = mean_se, geom = "ribbon", na.rm = T, size=ERRORBAR_THICKNESS/2, width=ERRORBAR_THICKNESS/2, alpha=0.3, color=NA) +
  stat_summary(fun="mean", geom="line", na.rm = T, alpha = 1, size=LINE_THICKNESS/4) +
  
  ylab('Phasic modulation') +
  xlab('Time re: spout withdrawal (s)') +
  
  scale_y_continuous(breaks=y_axis, expand=c(0, 0)) +
  
  scale_x_continuous(breaks=x_axis, expand=c(0, 0)) +
  
  coord_cartesian(ylim = c(min(y_axis), max(y_axis)), 
                  xlim = c(min(x_axis), max(x_axis))) +

  scale_color_manual(values = TRIALTYPE_MODULATION_COLORS) +
  scale_fill_manual(values = TRIALTYPE_MODULATION_COLORS)

  theme(
    strip.background = element_blank(),
    legend.position = 'none',
    panel.spacing = unit(2.5, "lines")
  ) +

p
```

### Stats
```{r echo=TRUE}
time_slice = c(0.3, 0.8)
df_grouped = auroc_df %>% group_by(Unit, Subject, TrialType, ActiveBaseline_modulation_direction) %>%
  summarise( 
    auroc_timeSlice_abs = mean(abs(auROC[(Time_s >= time_slice[1]) & (Time_s < time_slice[2])] - 0.5), na.rm=T)
  )
df_grouped$TrialType = factor(df_grouped$TrialType, levels=c('SpoutOff_hits_auroc', 'SpoutOff_FAs_auroc', 'SpoutOff_misses_auroc'))
levels(df_grouped$TrialType) = c('Hit', 'False alarm', 'Miss')
df_grouped$ActiveBaseline_modulation_direction = factor(df_grouped$ActiveBaseline_modulation_direction, levels=c('decrease', 'increase', 'none'))
levels(df_grouped$ActiveBaseline_modulation_direction) = c('Task-suppressed', 'Task-enhanced', 'Task-unchanged')

lme_data = df_grouped[df_grouped$ActiveBaseline_modulation_direction=='Task-suppressed',]
lme_bin <- glmmTMB((sqrt(auroc_timeSlice_abs))~ TrialType + (1 | Subject/Unit/TrialType),  data=lme_data, family=gaussian)
simulationOutput <- simulateResiduals(fittedModel = lme_bin, plot = T, re.form=NULL)  # pass
Anova(lme_bin)
pairs(regrid(emmeans(lme_bin,  ~TrialType)),  adjust='Bonferroni')

lme_data = df_grouped[df_grouped$ActiveBaseline_modulation_direction=='Task-enhanced',]
lme_bin <- glmmTMB((sqrt(auroc_timeSlice_abs))~ TrialType + (1 | Subject/Unit/TrialType),  data=lme_data, family=gaussian)
simulationOutput <- simulateResiduals(fittedModel = lme_bin, plot = T, re.form=NULL)  # pass
Anova(lme_bin)
pairs(regrid(emmeans(lme_bin,  ~TrialType)),  adjust='Bonferroni')

lme_data = df_grouped[df_grouped$ActiveBaseline_modulation_direction=='Task-unchanged',]
lme_bin <- glmmTMB((log(auroc_timeSlice_abs+0.1))*100~ TrialType + (1 | Subject/Unit/TrialType),  data=lme_data, family=gaussian)
simulationOutput <- simulateResiduals(fittedModel = lme_bin, plot = T, re.form=NULL)  # pass
Anova(lme_bin)
pairs(regrid(emmeans(lme_bin,  ~TrialType)),  adjust='Bonferroni')

```

## Fig S3C
```{r echo=TRUE, fig.height=10, fig.width=15, warning=FALSE}
# Plot the curves
graph_data = auroc_df[(auroc_df$Time_s >= -1) & (auroc_df$Time_s < 0) & auroc_df$TrialType != 'SpoutOff_misses_auroc',]
graph_data = graph_data[!is.na(graph_data$auROC),]
graph_data$TrialType = factor(graph_data$TrialType, levels=c('SpoutOff_hits_auroc', 'SpoutOff_FAs_auroc'))
levels(graph_data$TrialType) = c('Hit', 'False alarm')

graph_data$ActiveBaseline_modulation_direction = factor(graph_data$ActiveBaseline_modulation_direction, levels=c('decrease', 'increase', 'none'))
levels(graph_data$ActiveBaseline_modulation_direction) = c('Task-suppressed', 'Task-enhanced', 'Task-unchanged')

y_axis = seq(0.0, 0.25, 0.05)
x_axis = seq(-1, 0, 0.5)
p =ggplot(data=graph_data, aes(x=Time_s, y=abs(auROC-0.5), color=TrialType, fill=TrialType)) + 
  facet_grid(.~ActiveBaseline_modulation_direction) +
  stat_summary(fun.data = mean_se, geom = "ribbon", na.rm = T, size=ERRORBAR_THICKNESS/2, alpha=0.3, color=NA) +
  stat_summary(fun="mean", geom="line", na.rm = T, alpha = 1, size=LINE_THICKNESS/4) +
  
  ylab('Phasic modulation') +
  xlab('Time re: spout withdrawal (s)') +
  
  scale_y_continuous(breaks=y_axis, expand=c(0, 0)) +
  
  scale_x_continuous(breaks=x_axis, expand=c(0, 0)) +
  
  coord_cartesian(ylim = c(min(y_axis), max(y_axis)), 
                  xlim = c(min(x_axis), max(x_axis))) +

  scale_color_manual(values = TRIALTYPE_MODULATION_COLORS, name='') +
  scale_fill_manual(values = TRIALTYPE_MODULATION_COLORS, name='') +
    theme(
    strip.background = element_blank(),
    # strip.text.y = element_blank(),
    # strip.text.x = element_blank(),
    # axis.text.x.bottom = element_blank(),
    legend.position = c(0.85, 0.85),
    panel.spacing = unit(2.5, "lines")
  ) 
p
```

### Stats
```{r echo=TRUE}
time_slice = c(-0.5, 0)
df_grouped = auroc_df[auroc_df$TrialType %in% c('SpoutOff_hits_auroc', 'SpoutOff_FAs_auroc'),] %>% group_by(Unit, Subject, TrialType, ActiveBaseline_modulation_direction) %>%
  summarise( 
    auroc_timeSlice_abs = mean(abs(auROC[(Time_s >= time_slice[1]) & (Time_s < time_slice[2])] - 0.5), na.rm=T)
  )
df_grouped$TrialType = factor(df_grouped$TrialType, levels=c('SpoutOff_hits_auroc', 'SpoutOff_FAs_auroc'))
levels(df_grouped$TrialType) = c('Hit', 'False alarm')
df_grouped$ActiveBaseline_modulation_direction = factor(df_grouped$ActiveBaseline_modulation_direction, levels=c('decrease', 'increase', 'none'))
levels(df_grouped$ActiveBaseline_modulation_direction) = c('Task-suppressed', 'Task-enhanced', 'Task-unchanged')

lme_data = df_grouped[df_grouped$ActiveBaseline_modulation_direction=='Task-suppressed',]
lme_bin <- glmmTMB((log(auroc_timeSlice_abs+0.1))~ TrialType + (1 | Subject/Unit/TrialType),  data=lme_data, family=gaussian)
simulationOutput <- simulateResiduals(fittedModel = lme_bin, plot = T, re.form=NULL)  # pass
Anova(lme_bin)

lme_data = df_grouped[df_grouped$ActiveBaseline_modulation_direction=='Task-enhanced',]
lme_bin <- glmmTMB((log(auroc_timeSlice_abs+0.1))~ TrialType + (1 | Subject/Unit/TrialType),  data=lme_data, family=gaussian)
simulationOutput <- simulateResiduals(fittedModel = lme_bin, plot = T, re.form=NULL)  # pass
Anova(lme_bin)

lme_data = df_grouped[df_grouped$ActiveBaseline_modulation_direction=='Task-unchanged',]
lme_bin <- glmmTMB((log(auroc_timeSlice_abs+0.1))~ TrialType + (1 | Subject/Unit/TrialType),  data=lme_data, family=gaussian)
simulationOutput <- simulateResiduals(fittedModel = lme_bin, plot = T, re.form=NULL)  # pass
Anova(lme_bin)
```
